The problem and promise of scale in multilayer networks

### 2019-09-11 paper/unstructured.Rmd
rm temp variables
fin skeleton

@@

## Boxes / paper layout

* Abstract
* Intro
* Box 1: Mathematical + language definitions of multilayer networks
* Box 2: Types of spatiotemporally explicit data and considerations relevant to these e.g. fix rate/grouping with GPS and gambit of the group, etc (table)
* Spatial variables - example of GPS data, sampling landcover and networks across landcover classes?
* Temporal variables - example of GoG data, chunked seasonally maybe?
* Relevant multilayer metrics with above two? 
* Conclusion/fin

>>>>

**Conservation implications**

@@

## Skeleton
* Abstract
* Brief introduction
  * Networks, social networks, animal social systems 
  * Landscape ecology, scale
* Multilayer Networks
  * What is a ML network
  * What kinds of ML nets exist
  * Which are relevant to spatial variables
* Scale 
  * What is scale
  * In LE lit, how has scale been investigated
  * Elements of scale relevant to animal social systems, animal movement data, landcover data
* Box 1: Types of spatiotemporally explicit data and considerations relevant to these e.g. fix rate/grouping with GPS and gambit of the group, etc (table)
* Box 2: Mathematical + language definitions of multilayer networks, metrics and measures of ML networks that are relevant to spatial data
* Simulations
* Discussion/results
* Brief conclusion

---

From a sample of CZ papers:

* Abstract
* Materials and Methods
* Results
* Discussion

and sometimes
* Conservation implications
* Conclusion
